% !TEX root = system_validation.tex

\subsection{Localization}
\label{sec:verification_localization}

\subsubsection{Performance Test: Robot Position Accuracy}
\label{test:localization_pt_accuracy}
\textbf{Test Question:} Is the localization system able to accurately determine the position of each robot?\\
\textbf{Operational Procedure:} Both robots sit stationary within the working bounds. The localization system then attempts to determine their locations.\\
\textbf{Metric:} The difference of the robot's actual position from the position reported by the localization system. \\
\textbf{Acceptance Criteria:} The reported position must be within 1/10 in. of the actual position.\\
\textbf{Requirement(s) Verified:} NF6, FR4 \\
\result{We were able to accurate detect each robot.}

\subsubsection{Performance Test: Bounds Accuracy}
\label{test:localization_pt_bounds}
\textbf{Test Question:} Is the localization system able to accurately determine the boundaries of the workspace?\\
\textbf{Operational Procedure:} The localization system attempts to determine the bounds of the workspace.\\
\textbf{Metric:} The total difference in distance between the reported corners of the workspace and the distance between the actual corners.\\
\textbf{Acceptance Criteria:} The total difference must not exceed 1 in.\\
\textbf{Requirement(s) Verified:} FR4 \\
\result{We were able to accurately detect the bounds.}

\subsubsection{Functional Test: Robot Position}
\label{test:localization_ft_robopos}
\textbf{Test Question:} Can the localization system find the robot?\\
\textbf{Operational Procedure:} With a single robot within the working bounds, the localization system attempts to determine the robot's location. Robot operation out of bounds is also considered out of scope, and is undefined behavior.\\
\textbf{Metric:} Whether or not a location is returned by the localization system.\\
\textbf{Acceptance Criteria:} The system must return a location for the robot. \\
\textbf{Requirement(s) Verified:} FR4, NFR6, FR3, NFR13 \\
\result{We were able to localize each robot.}

\subsubsection{Functional Test: Bounds}
\label{test:localization_ft_bounds}
\textbf{Test Question:} Can the localization system find the working bounds?\\
\textbf{Operational Procedure:} The localization system attempts to find all four corners of the working bounds while they are all in its field of view.\\
\textbf{Metric:} Whether or not locations are returned for all four corners.\\
\textbf{Acceptance Criteria:} The system must return locations for all four corners of the working bounds.\\
\textbf{Requirement(s) Verified:} FR4, NFR6, FR3 \\
\result{We received all four corners.}
