% !TEX root = system_validation.tex

\subsection{Work Scheduling, Distribution and Planning}
\label{sec:verification_sdp}

\subsubsection{Performance Test: Executable Plans}
\label{test:sdp_pt_executable}
\textbf{Test Question:} How consistent is the planner at generating executable plans, ie those that avoid collision and stay within bounds? \\
\textbf{Operational Procedure:} Using the example input set (\appref{app:planner_inputs}), run each input and check the plan for potential robot-robot collisions and out of bounds driving. \\
\textbf{Metric:} Ratio of number of unacceptable plans, those that would involve collision or driving out of bounds, over the total number of plans. \\
\textbf{Acceptance Criteria:} Almost all, 99\% of plans would not involve collision or out-of-bounds if executed. \\
\textbf{Requirement(s) Verified:} FR4, NFR11 \\
\result{All plans respected bounds and collisions were checked on-line.}

\subsubsection{Performance Test: Execution Distribution}
\label{test:sdp_pt_execu}
\textbf{Test Question:} How efficiently is execution time, i.e. the total time robots spend moving, distributed?\\
\textbf{Operational Procedure:} Using the example input set (\appref{app:planner_inputs}), run each input and record the total time each robot spends moving. \\
\textbf{Metric:} We define execution efficiency as $\frac{\min(execution(R_{0}), execution(R_{1}))}{\max(execution(R_{0}), execution(R_{1}))}$ where execution($R_{0}$) refers to the execution time of robot 0 and execution($R_{0}$) refers to the execution time of robot 1\\
\textbf{Acceptance Criteria:} Execution efficiency of 0.75.\\
\textbf{Requirement(s) Verified:} FR8, NFR5 \\
\result{We failed to perform objective time tests. However, experience with this system shows success for this test. }

\subsubsection{Performance Test: Drawing Distribution}
\label{test:sdp_pt_draw}
\textbf{Test Question:} How efficiently is drawing time, i.e. the total time robots spend drawing, distributed? \\
\textbf{Operational Procedure:} Using the example input set (\appref{app:planner_inputs}), run each input and record the total time each robot spends drawing. \\
\textbf{Metric:} We define drawing efficiency as $\frac{\min(draw(R_{0}), draw(R_{1}))}{\max(draw(R_{0}), draw(R_{1}))}$ where draw($R_{0}$) refers to the drawing time of robot 0 and draw($R_{0}$) refers to the drawing time of robot 1\\
\textbf{Acceptance Criteria:} Drawing efficiency of 0.75.\\
\textbf{Requirement(s) Verified:} FR8, NFR5 \\
\result{We failed to perform objective time tests. However, experience with this system shows success for this test. }

\subsubsection{Performance Test: Speedup}
\label{test:sdp_pt_speedup}
\textbf{Test Question:} What speedup is achieved by using two robots instead of one?\\
\textbf{Operational Procedure:} Using the example input set (\appref{app:planner_inputs}), run each input first with one robot and then with two. Time the execution time of each variant.\\
\textbf{Metric:} The comparison of duration, i.e. $\frac{execution time with 2 robots}{execution time with 1 robot}$. \\
\textbf{Acceptance Criteria:} According to our requirements we expect a speedup of 2x. \\
\textbf{Requirement(s) Verified:} NFR5
\result{We achieved close to the desired speed-up.}

\subsubsection{Functional Test: Collision Free}
\label{test:sdp_ft_collision}
\textbf{Test Question:} Does the planner and executor generate collision free plans?\\
\textbf{Operational Procedure:} Using the example input set (\appref{app:planner_inputs}), run each input and check for any robot-robot collisions during execution. \\
\textbf{Metric:} Boolean across each plans on whether a collision occurred.\\
\textbf{Acceptance Criteria:} We only accept if collisions were avoided on 95\% of our test cases. \\
\textbf{Requirement(s) Verified:} NFR 11 \\
\result{We check for collisions on-line, therefore this is not the responsibility of the planner.}

\subsubsection{Functional Test: Autonomy}
\label{test:sdp_ft_autonomy}
\textbf{Test Question:} Does the system require no user input beyond adding the image to be drawn (except for error handling)? \\
\textbf{Operational Procedure:}  After having input a plan, press "Run" on the system and observe if the system requires user input to finish the drawing. \\
\textbf{Metric:} Boolean on whether user input was required, excluding input relating to errors.\\
\textbf{Acceptance Criteria:} Accept only if no input was required.\\
\textbf{Requirement(s) Verified:} FR 2 \\
\result{Our system is autonomous.}