% !TEX root = main.tex

\section{Build Progress}
\label{sec:build_progress}

This section details system development and progress made since the last milestone presentation. Progress is split into three major sections: electromechanical, software, and integration. Electromechanical updates detail chassis build progress, as well as setup of the electronics to drive the motors for locomotion and using the writing implement. Software updates describe progress towards subsystem completion. Integration details updates made with regard to integrating the electromechanical and software systems, and testing functionality.

\subsection{Electromechanical Updates}
\label{sec:electromechanical_progress}

\subsubsection{Electrical Updates}
\label{sec:electrical_progress}
As shown below in \figref{fig:em1}, we have built a physical robot prototype that incorporates chassis, painting mechanism, and locomotion system. The chassis is made of laser patterned acrylic. It is designed to be compact, as possible because smaller robots are less likely to collide with each other during drawing operations. This prototype proves that the chassis’ current cutout sizes have no clearance issues with moving components. 

\subsubsection{Mechanical Updates}
\label{sec:mechanical_progress}

\yjnote{Talk about webcam jig}
\yjnote{Building new robot, motor shafts, etc.}



\subsection{Software Update}
\label{sec:software_progress}
We detail the software progress made across the following subsystems. Most subsystems have reached the point of usability, and at this point most additions enhance ease-of-use and functionality.


\subsubsection{Locomotion}
The locomotion subsystem has been fully implemented as a part of the onboard controller code. The subsystem is capable of determining motor commands based on a target vector direction to move the robot along the specified vector.

\subsubsection{Localization}


\subsubsection{Scheduling, Distribution and Planning (SDP)}

\subsubsection{User Interface}


\subsection{Integration Updates}
\label{sec:integration_progress}

\clearpage
