% !TEX root = main.tex

\section{Locomotion}
\label{sec:locomotion}
\njnote{THIS IS WRONG. Needs to talk about holonomic and mecanum}
\textbf{Description:} The robot's locomotion system propels each individual robot across the working surface. If the robot uses a holonomic locomotion system, they are able to move in any direction, ensuring their ability to execute intricate designs. \added[remark={DZ, V2}]{Mechanum wheels will allow the robots that flexibility, while at the same time preserving stability and ease of control.} They also provide enough clearance for the writing implement to work effectively. In the case of a tread-based locomotion system, individual robots can rotate in place to move in all directions. A driving system that allows for multidirectional movement satisfies motion-related requirements (Requirements Specification, 5.1, FR7). Additionally, the locomotion system contains encoders whose data is used by the localization module (\sref{sec:localization}). \\

\noindent
\textbf{Critical Components:} Wheels or treads, motors and encoders.

\rhnote{Comment from DW: "This description of the locomotion hardware is insufficient. How does it work? There is not enough information and analysis to move into a detailed design of how it would be built." Will the trade study address this?}

\subsection{Use Cases}
\subsubsection{Locomote}
\textbf{Description:} \added[remark={DZ, V2}]{The robot can use its array of motors and wheels to propel itself across the flat working surface. It can make arbitrarily sharp turns and acute curves in order to allow input drawings that incorporate such components. }

\subsection{Trade Study}
\label{sec:trade_locomotion}
One of our functional requirements with the highest priority (FR1) is to be able to move in specified directions with a high degree of accuracy. Additionally, a medium high priority functional requirement (FR 9) is to have a drive control system that enables this movement. Therefore, it is clear from our requirements that locomotion is critical to our robot's performance. When considering locomotion options there are three large categories: aerial, legged and wheeled. 

Our drawing occurs on the two dimensional plane. Therefore, any flight based system would have to constrain one translational degree of freedom and two rotational degrees of freedom. Doing so would require precise control algorithm and large power input. Practically speaking, this seems to over-complicate the problem with little additional gain. 

Therefore, we are narrowed down to a legged or wheeled system. While a legged system would have the ability to traverse uneven terrain, such capability is not necessary for our project due to the assumption (A3) that the drawing surface is flat and homogenous. Compared to wheeled systems, legged systems usually involve more complicated control algorithms and electrical and mechanical components. In addition, legged system often fail to ensure stability in robot body where holds the drawing implement. Considering system complexity and locomotion stability, we have concluded that our agent's drive system should be wheeled. In our next analysis, we will further investigate different types of drive system. 

In continuing to prioritize our functional requirement (FR1) of being able to accurately move in specified directions, we further investigate possible drive systems. Four different drive systems are evaluated: differential drive, Ackerman steering, four-wheel steering, and holonomic drive. \added[remark={YJ, V2}]{Each of the four drive systems are evaluated based on mobility, motion accuracy and amount of damage to drawing surfaces.

Differential drive typically consists of two independently driven wheels and a non-driven wheel. Such drive system has good mobility due to its minimum number of driving wheels. However, the non-driven wheel often creates unwanted resistance while turning which both compromises the drawing accuracy and damages drawing surfaces. Occasionally, the non-driven wheel would fall in singularity position and ruin the drawing mission.

Moving up in complexity and taking after some cars is Ackerman steering, where the back pair of wheels is fixed in orientation but the front pair can pivot. Such drive system does not suffer from singularities and does not damage drawing surfaces. However, turning with ackerman steering often requires large turning radius, which makes drawing shape corners extremely difficult. Therefore, despite it has high motion accuracy and minimum amount of damage to drawing surfaces, Ackerman steering ranks low in mobility.

Another option is four-wheel steering, which is similar to Ackerman steering but allows the back wheels to pivot. Even though such drive system can achieve in-place turn, doing so often requires statically pivoting wheels, which can potentially damage drawing surfaces. Hence, four-wheel steering ranks high in mobility and motion accuracy, but low in damage to drawing surfaces.

Holonomic drive involves independent control of four omnidirectional wheels. Such drive system can easily turn in place and does not cause any potential damage to drawing surfaces. The drive system's motion accuracy depends on wheel choice. Holonomic drive is often achieved with either omniwheels or mecanum wheels. Omniwheel does not resist any force in its lateral direction, resulting in low motion accuracy. Mecanum wheel, on the other hand, would resist sideway disturbance and ensure straightness of lines due to the wheel's obliquely oriented rollers.

In conclusion, the system's locomotion system would be a wheeled holonomic drive system with mecanum wheels, since such combination better satisfies system requirements and performs best in criteria concerning mobility, motion accuracy, and amount of damage to drawing surfaces.}

\subsection{Artistic Sketch}
\njnote{Description of sketch and how it relates to trade studies above}

\subsection{Requirements Fulfilled}
\added[remark={RH, V2}]{By using mecanum wheels, we can achieve omnidirectional movement (FR1) and reliable control (FR9). Our emergency stop (FR13) and error handling (NFR2) will be integrated into the drive system through the communication network \sref{sec:communication}. Our mecanum wheels have been specificed to stay within our weight (NFR3), size (NFR4) and budget (NFR10) limits. The control of the mecanums will allow us to be efficient (NFR5), due to their omnidirectional motion and speed, while maintaining quality (NFR6), reliability (NFR8) and safety (NFR11). Additionally the omnidirectional control wil allow us positional (NFR12) and rotational (NFR13) accuracy.}
