\documentclass[a4paper,10pt]{article}
%\documentclass{spec}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage[margin=1in]{geometry}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{float}
\usepackage{ifthen,version}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}

% Tracking Changes
%\usepackage[final]{changes}
\usepackage{changes}
%\definechangesauthor[name={Per cusse}, color=orange]{per}
\setremarkmarkup{(#2)}

% Labels in IEEE format
\newcommand{\sref}[1]{Sec. \ref{#1}} % Section
\newcommand{\figref}[1]{Fig.\ref{#1}} % Figure
\newcommand{\frref}[1]{FR\ref{#1}} % Functional Requirement

\usepackage{ifthen}
\newboolean{include-notes}
\setboolean{include-notes}{true}
\newcommand{\njnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{orange}{\textbf{NJ: #1}}}{}}
\newcommand{\rhnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{red}{\textbf{RH: #1}}}{}}
\newcommand{\dznote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{green}{\textbf{DZ: #1}}}{}}
\newcommand{\yjnote}[1]{\ifthenelse{\boolean{include-notes}}
 {\textcolor{LimeGreen}{\textbf{YJ: #1}}}{}}

\begin{document}

\begin{titlepage}
	\centering
	{\scshape\LARGE Carnegie Mellon University \par}
	\vspace{1cm}
	{\scshape\Large Robotics Capstone Project\par}
	\vspace{1.5cm}
	{\huge\bfseries Concept Design\par}
	\vspace{2cm}
	{\Large\itshape Friction Force Explorers:\par}
	\vspace{1cm}
	{\Large\itshape Don Zheng\par}
	{\Large\itshape Neil Jassal\par}
	{\Large\itshape Yichu Jin\par}
	{\Large\itshape Rachel Holladay\par}
	\vfill
	supervised by\par
	Dr.~David \textsc{Wettergreen}

	\vfill

% Bottom of the page
	{\large Version 2.0\par
	\today\par}
\end{titlepage}

\tableofcontents
\listoffigures
\clearpage

%This is \added[remark={has to be in it}]{new} text.
%This is \deleted[remark=obsolete]{unnecessary}text.
%This is \replaced[remark={bad wording}]{nice}{bad} text.

\rhnote{Need to fix references in system description and concept operation. Need to full in subsystem listing. Need fix each subsystem description. Need to add requirements fulfilled. Need to add artistic sketch + trade study. Need to add research for planning.}
\input{system_description.tex}   % Edit complete
\input{concept_operation.tex}    % Edit complete
\input{subsystem_listing.tex}

\input{writing_implement.tex}
\input{locomotion.tex} done
\input{localization.tex}
\input{image_processing.tex} 
\input{planning.tex}
\input{communication.tex} 
\input{user_interface.tex}
\input{power_system.tex} 
\input{install.tex} 
\input{requirements_table.tex}

%\input{use_cases.tex}
%\input{artistic_sketch.tex}

%\pagebreak
%\listofchanges
%\pagebreak

{\footnotesize
\bibliographystyle{ieeetr}
\bibliography{references}}

\end{document}
