% !TEX root = system_validation.tex

\subsection{Power System}
\label{sec:verification_power}

\subsubsection{Performance Test: Battery Duration}
\label{test:power_pt_battery}
\textbf{Test Question:} How long can an individual robot run for on a single battery charge? \\
\textbf{Operational Procedure:} Charge a robot fully. Given some example drawing inputs, continue to input drawings until the robot is fully drained of power. Time how long this takes. \\
\textbf{Metric:} The duration of operational time given one charge \\
\textbf{Acceptance Criteria:} We accept this if the operational time exceeds the necessary duration time of 90\% of our test drawing inputs. \\
\textbf{Requirement(s) Verified:} \frref{fr:battery_power}

\subsubsection{Functional Test: Battery Life}
\label{test:power_ft_battery}
\textbf{Test Question:} Can the robots complete a drawing from a single charge? \\
\textbf{Operational Procedure:} Given a set of example drawing inputs, we want to test the robots ability. For each input, fully charge each robot, send the input and keep track of whether the drawing is fully complete before the battery on either robot is fully drained. \\
\textbf{Metric:} The ratio of the number of completed drawings to the total number of drawings. \\
\textbf{Acceptance Criteria:}  We want to be able to successfully draw 90\% of the drawings in our example drawing input set. \\
\textbf{Requirement(s) Verified:} \frref{fr:battery_power}


\subsubsection{Failure Mode: Insufficient Battery}
\label{sec:power_fm_battery}
\textbf{Description:} This failure mode arises when the battery for an individual robot agent is low or out of power.\\
\textbf{Cause:} Insufficient battery power is a result of overuse of the battery from autonomously drawing for too long.\\
\textbf{Effect:} The result is a robot agent being unable to move, draw, or communicate with the offboard system, as it has no subsystems being powered.\\
\textbf{Criticality:} This failure is critical, as it can pause and/or end robot operation. Robot agent battery must be replaced before operation can continue.\\
\textbf{Safety Hazards:} There are no safety hazards that result from the battery being low or out of power.