% !TEX root = main.tex

\section{Failure States and Recovery}
\label{sec:failure_states}
\subsection{Degraded Mode: Driving but Not Drawing}
This failure state occurs when a robot agent is able to drive properly using localization and planning but the writing implement is not working properly. It can be caused by one of two factors: a broken actuation mechanism, or the writing material is out of ink. The writing implement running out of ink is significantly more likely, as it is a common occurrence and the system is designed around this limitation. For either degraded mode, the only solution is for the user to pause system operation, resolve the issue, and resume operation. The user can either replace the writing implement or replenish ink, or fix the actuation mechanism. This mode can be traced back to the following failure modes from the Test Plan: \failref{sec:failure_writing_implement}, \failref{sec:sdp_fm_planning}, \failref{sec:comm_fm_loss}.

\subsection{Degraded Mode: Erratic Driving or Drawing}
Erratic driving or drawing occurs when the robot is moving, but not responding properly to the given commands. It can also occur when the commands being sent are incorrect, or when the drawing actuation commands or actuation is incorrect. Invalid motion can be attributed to the system failing to move omnidirectionally (likely due to issues with one or more mecanum wheels), or due to external factors such as slippage. Incorrect commands and undefined behavior can begin as a result of incorrect localization, loss of connection between offboard and onboard systems, battery problems, or the robot agent moving out of bounds. In these situations, the solution is to end system operation. Undefined behavior cannot be resolved without resetting the system. \added[remark={NJ, V2}]{This mode can be traced back to the following failure modes from the Test Plan:} \failref{sec:writing_fm_mechanism}, \failref{sec:locomotion_fm_motion}, \failref{sec:locomotion_fm_omni}, \failref{sec:localization_fm_unusable}, \failref{sec:localization_fm_occlusion}, \failref{sec:comm_fm_incorrect}, \failref{sec:power_fm_battery}.

\subsection{Degraded Mode: Planning Failure}
Planning failure is a degraded mode that occurs when the input image is unable to be processed into a path. When this happens, the planner is unable to generate a set of paths for the robot agents. The system cannot begin to draw the image without a valid path, so the user is required to enter a new image to begin system operation. \added[remark={NJ, V2}]{This test plan can be traced back to the following failure modes from the Test Plan:} \failref{sec:sdp_fm_planning}.
