% !TEX root = system_validation.tex

\subsection{Power System}
\label{sec:failure_power}

\subsubsection{Insufficient Battery}
\label{sec:power_fm_battery}
\added[remark={RH, V2}]{\textbf{Description:} This failure mode arises when the battery for an individual robot agent is low or out of power.}\\
\added[remark={RH, V2}]{\textbf{Cause:} Insufficient battery power is a result of overuse of the battery from autonomously drawing for too long.}\\
\added[remark={RH, V2}]{\textbf{Effect:} The result is a robot agent being unable to move, draw, or communicate with the offboard system, as it has no subsystems being powered.}\\
\added[remark={RH, V2}]{\textbf{Criticality:} This failure is critical, as it can pause and/or end robot operation. Robot agent battery must be replaced before operation can continue.}\\
\added[remark={RH, V2}]{\textbf{Safety Hazards:} There are no safety hazards that result from the battery being low or out of power.}\\
\added[remark={DZ, V2}]{\textbf{Mitigation:} Regular battery level inspections and using reliable batteries can help mitigate this failure mode.}

\subsection{Battery Explosion}
\label{sec:power_fm_explosion}
\added[remark={DZ, V2}]{\textbf{Description:} This failure mode arises when the battery experiences catastrophic failure and EXPLODES.}\\
\added[remark={DZ, V2}]{\textbf{Cause:} Improper charging procedures or unsafe battery handling can cause this failure mode to occur.}\\
\added[remark={DZ, V2}]{\textbf{Effect:} Battery explosion can cause irreparable damage to the entire system, as well as to the humans in the area.}\\
\added[remark={DZ, V2}]{\textbf{Criticality:} This failure is of high importance. Battery explosion will cause the entire system to become unusable, and will undoubtedly require an extensive amount of work to repair.}\\
\added[remark={DZ, V2}]{\textbf{Safety Hazards:} There is a significant safety hazard for this failure mode, as with all situations involving fire and explosions.}\\
\added[remark={DZ, V2}]{\textbf{Mitigation:} Strict procedures for battery charging and handling can help mitigate this failure mode.}\\